Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?

### 2022-09-04 Paper.Rmd
this has to be the final outline

Any website which offers online reviews for products were used as a data source (Yelp, Booking, BestBuy, eBay) in the literature of review helpfulness but the majority of the aforementioned studies used the data from either websites Amazon or Internet Movie Database (IMDB) because these websites offer relatively easier ways to get the needed data. They have their respective APIs and on top of that, it is relatively easier to scrape both websites. Additionally, both websites offer product reviews for a numerous different types of products. Amazon is a huge e-retailer and offers a wide range of items. IMDB is a home for both critic and user reviews of Movies and TV Shows. In some other studies local equivalents of Amazon was used as well. [@sun2019]. @cao2011 used data from CNET Download.com which is a software distributor.

@@

@@

# Discussion and Conclusion

>>>>

Any website which offers online reviews for products could be used as a data source (Yelp, Booking, BestBuy, eBay) in the literature of review helpfulness but the majority of the aforementioned studies used the data from either websites Amazon or Internet Movie Database (IMDB) because these websites offer relatively easier ways to get the needed data. They have their respective APIs and on top of that, it is relatively easier to scrape both websites. Additionally, both websites offer product reviews for a numerous different types of products. Amazon is a huge e-retailer and offers a wide range of items. IMDB is a home for both critic and user reviews of Movies and TV Shows. In some other studies local equivalents of Amazon was used as well. [@sun2019]. @cao2011 used data from CNET Download.com which is a software distributor.

There might be variety reasons why there are some conflicting results in the literature. First of all, many different data sources were used in the studies. Even in the same data source, for instance Amazon, there exist a wide range of products with different brands. Different sub-groups of products can receive different feedbacks. This might increase the potential noise in the data, leading conflicting results. Secondly, many different research designs and research methodologies were employed. In these different research designs different independent and control variables were used because the data at the hand may allow for different sets of variables. Lastly, there is no established theory of review helpfulness. This means that studies are rather unorganized and researchers are usually inclining towards their own domain of expertise when it comes to explaining review helpfulness.

@@

## Some other theory

@@

# Discussion

# Conclusion
